---
title: "LACrime2"
author: "Alcen Chiu"
date: "2023-05-22"
output: pdf_document
---

```{r setup, include=FALSE}
install.packages("dplyr")
install.packages("ggplot2")
install.packages("knitr")
library(dplyr)
library(ggplot2)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r reading in data}
NO10 <- read.csv("NewOrleans_Incident_2010_geo_MT.csv")
NO11 <- read.csv("NewOrleans_Incident_2011_geo_MT.csv")
NO12 <- read.csv("NewOrleans_Incident_2012_geo_MT.csv")
NO13 <- read.csv("NewOrleans_Incident_2013_geo_MT.csv")
NOcensus <- read.csv("NOcensus.csv")

write.csv(NOmeanoccurences, "C:\\Users\\alcenchiu\\Downloads\\FIPS.csv", row.names = FALSE)
```

```{r crime frequency in FIPS}
# finding the number of occurences and frequency for each FIP
crimebyFIPS10 <- NO10 %>%
  group_by(FIPS) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
crimebyFIPS11 <- NO11 %>%
  group_by(FIPS) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
crimebyFIPS12 <- NO12 %>%
  group_by(FIPS) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
crimebyFIPS13 <- NO13 %>%
  group_by(FIPS) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
# joining the FIP occurences and frequency by FIPS across all years
NOjointdataset <- merge(crimebyFIPS10, crimebyFIPS11, by = 'FIPS')
NOjointdataset <- merge(NOjointdataset, crimebyFIPS12, by = 'FIPS')
NOjointdataset <- merge(NOjointdataset, crimebyFIPS13, by = 'FIPS')
colnames(NOjointdataset) <- c('FIPS', '2010 Occurences', '2010 Frequency', '2011 Occurences', '2011 Frequency', '2012 Occurences', '2012 Frequency', '2013 Occurences', '2013 Frequency')
NOjointoccurences <- NOjointdataset %>% select('2010 Occurences','2011 Occurences','2012 Occurences','2013 Occurences')
# calculating the mean number of occurence from 2010-2013
NOjointoccurences$'Mean Occurence/Year' = rowMeans(NOjointoccurences, na.rm=TRUE)
NOmeanoccurences <- data.frame(NOjointdataset$FIPS, NOjointoccurences$'Mean Occurence/Year')
colnames(NOmeanoccurences) <- c('FIPS', 'Mean Occurence/Year')
```

```{r transposing data NEW}
#splitting the census data into income data
NOcensus <- NOcensus[-c(1), ]
NOincome <- NOcensus %>% select(FIPS, Households., Households..Less.than..10.000, Households...10.000.to..14.999, Households...15.000.to..19.999, Households...20.000.to..24.999, Households...25.000.to..29.999, Households...30.000.to..34.999, Households...35.000.to..39.999, Households...40.000.to..44.999, Households...45.000.to..49.999, Households...50.000.to..59.999, Households...60.000.to..74.999, Households...75.000.to..99.999, Households...100.000.to..124.999, Households...125.000.to..149.999, Households...150.000.to..199.999, Households...200.000.or.More)
NOpercentincome <- NOcensus %>% select(FIPS, X..Households..Less.than..10.000, X..Households...10.000.to..14.999, X..Households...15.000.to..19.999, X..Households...20.000.to..24.999, X..Households...25.000.to..29.999, X..Households...30.000.to..34.999, X..Households...35.000.to..39.999, X..Households...40.000.to..44.999, X..Households...45.000.to..49.999, X..Households...50.000.to..59.999, X..Households...60.000.to..74.999, X..Households...75.000.to..99.999, X..Households...100.000.to..124.999, X..Households...125.000.to..149.999, X..Households...150.000.to..199.999, X..Households...200.000.or.More)
# splitting the census data in race data
NOrace <- NOcensus %>% select(FIPS, Total.Population, Total.Population..Not.Hispanic.or.Latino..White.Alone, Total.Population..Not.Hispanic.or.Latino..Black.or.African.American.Alone, Total.Population..Not.Hispanic.or.Latino..American.Indian.and.Alaska.Native.Alone, Total.Population..Not.Hispanic.or.Latino..Asian.Alone, Total.Population..Not.Hispanic.or.Latino..Native.Hawaiian.and.Other.Pacific.Islander.Alone, Total.Population..Not.Hispanic.or.Latino..Some.Other.Race.Alone, Total.Population..Not.Hispanic.or.Latino..Two.or.More.Races, Total.Population..Hispanic.or.Latino)
NOpercentrace <- NOcensus %>% select(FIPS, X..Total.Population..Not.Hispanic.or.Latino..White.Alone, X..Total.Population..Not.Hispanic.or.Latino..Black.or.African.American.Alone, X..Total.Population..Not.Hispanic.or.Latino..American.Indian.and.Alaska.Native.Alone, X..Total.Population..Not.Hispanic.or.Latino..Asian.Alone, X..Total.Population..Not.Hispanic.or.Latino..Native.Hawaiian.and.Other.Pacific.Islander.Alone, X..Total.Population..Not.Hispanic.or.Latino..Some.Other.Race.Alone, X..Total.Population..Not.Hispanic.or.Latino..Two.or.More.Races, X..Total.Population..Hispanic.or.Latino)
# transposing the race data from wide to long
NOrace_long <- gather(NOrace, Race, People, Total.Population..Not.Hispanic.or.Latino..White.Alone:Total.Population..Hispanic.or.Latino, factor_key=TRUE)
NOpercentrace_long <- gather(NOpercentrace, PercentRace, Share, X..Total.Population..Not.Hispanic.or.Latino..White.Alone:X..Total.Population..Hispanic.or.Latino, factor_key=TRUE)
NOjointrace <- cbind(NOrace_long, NOpercentrace_long)
# joining transposed race data with income data
NOjointincomerace <- cbind(NOjointrace, NOincome, NOpercentincome)
# transposing income data to align with transposed race data
NOjointincomerace1 <- gather(NOjointincomerace, IncomeBin, Households, Households..Less.than..10.000:Households...200.000.or.More, factor_key = TRUE )
NOjointincomerace1 <- NOjointincomerace1 %>% select(-5, -8, -10) 
NOjointincomerace1 <- NOjointincomerace1 %>% arrange(pick(FIPS))
NOjointincomerace1 <- NOjointincomerace1 %>% select(FIPS, Race, People, PercentRace, Share, IncomeBin, Households)
NOjointincomerace2 <- gather(NOjointincomerace, PercentIncomeBin, IncomeShare,X..Households..Less.than..10.000:X..Households...200.000.or.More, factor_key = TRUE )
NOjointincomerace2 <- NOjointincomerace2 %>% select(-5, -8, -26) 
NOjointincomerace2 <- NOjointincomerace2 %>% arrange(pick(FIPS))
NOjointincomerace3 <- NOjointincomerace2 %>% select(FIPS, Race, People, PercentRace, Share, PercentIncomeBin, IncomeShare)
NOjointincomerace4 <- NOjointincomerace3 %>% select(PercentIncomeBin, IncomeShare)
NOjointincomerace5 <- cbind(NOjointincomerace1, NOjointincomerace4)
# creating a new column calculating income share by race share
NOjointincomerace5$Share <- as.numeric(NOjointincomerace5$Share)
NOjointincomerace5$IncomeShare <- as.numeric(NOjointincomerace5$IncomeShare)
NOjointincomerace5$Share <- NOjointincomerace5$Share/100
NOjointincomerace5$IncomeShare <- NOjointincomerace5$IncomeShare/100
NOjointincomerace5$IncomexRaceShare <- NOjointincomerace5$Share*NOjointincomerace5$IncomeShare
NOjointincomerace5$Households <- as.numeric(NOjointincomerace5$Households)
NOjointincomerace5$IncomexRaceShare <- as.numeric(NOjointincomerace5$IncomexRaceShare)
NOjointincomerace5$NewHouseholds <- (NOjointincomerace5$Households / NOjointincomerace5$IncomeShare) * (NOjointincomerace5$IncomexRaceShare)
```

```{r final data}
# each row is a tract by race by income bin
NOFinalData <- merge(NOjointincomerace5, NOmeanoccurences, by = "FIPS")
NOpopulation <- NOrace %>% select(FIPS, Total.Population)
NOFinalData2 <- merge(NOFinalData, NOpopulation, by = "FIPS")
NOFinalData2$'Mean Occurence/Year' <- as.numeric(NOFinalData2$'Mean Occurence/Year')
NOFinalData2$Total.Population <- as.numeric(NOFinalData2$Total.Population)
NOFinalData2$'Crime/Capita' <- NOFinalData2$'Mean Occurence/Year'/ NOFinalData2$Total.Population

NOFinalData2 <- NOFinalData2 %>%
  mutate(IncomeBin = recode(IncomeBin, Households..Less.than..10.000 = '1', Households...10.000.to..14.999 = '2', Households...15.000.to..19.999 = '3', Households...20.000.to..24.999 = '4', Households...25.000.to..29.999 = '5', Households...30.000.to..34.999 = '6', Households...35.000.to..39.999 = '7', Households...40.000.to..44.999 = '8', Households...45.000.to..49.999 = '9', Households...50.000.to..59.999 = '10', Households...60.000.to..74.999 = '11', Households...75.000.to..99.999 = '12', Households...100.000.to..124.999 = '13', Households...125.000.to..149.999 = '14', Households...150.000.to..199.999 = '15', Households...200.000.or.More = '16'))
NOFinalData2$Income <- NOFinalData2$IncomeBin
NOFinalData2 <- NOFinalData2 %>%
  mutate(Income = recode(Income, '1' = '5000', '2' = '12500', '3' = '17500', '4' = '22500', '5' = '27500', '6' = '32500', '7' = '37500', '8' = '42500', '9' = '47500', '10' = '55000', '11' = '67500', '12' = '87500', '13' = '112500', '14' = '137500', '15' = '175000', '16' = '240000'))
NOFinalData2 <- NOFinalData2 %>% relocate('Income', .after = IncomeBin)
NOFinalData2$IncomePercentile <- NOFinalData2$IncomeBin
NOFinalData2 <- NOFinalData2 %>% relocate('IncomePercentile', .after = Income)
NOFinalData2 <- NOFinalData2 %>%
  mutate(IncomePercentile = recode(IncomePercentile, '1' = 3.0, '2' = 8.15, '3' = 12.5, '4' = 17.0, '5' = 21.5, '6' = 25.9, '7' = 30.3, '8' = 34.5, '9' = 38.5, '10' = 44.0, '11' = 52.8, '12' = 64.0, '13' = 74.9, '14' = 82.5, '15' = 88.9, '16' = 96.1))
NOFinalData2 <- NOFinalData2 %>%
  mutate(Race = recode(Race, Total.Population..Not.Hispanic.or.Latino..White.Alone = 'White', Total.Population..Hispanic.or.Latino = 'Hispanic/Latino', Total.Population..Not.Hispanic.or.Latino..Black.or.African.American.Alone = 'Black/African American', Total.Population..Not.Hispanic.or.Latino..American.Indian.and.Alaska.Native.Alone = 'American Indian/Alaska Native', Total.Population..Not.Hispanic.or.Latino..Asian.Alone = 'Asian', Total.Population..Not.Hispanic.or.Latino..Native.Hawaiian.and.Other.Pacific.Islander.Alone = 'Native Hawaiian/Pacific Islander', Total.Population..Not.Hispanic.or.Latino..Some.Other.Race.Alone = 'Other Race', Total.Population..Not.Hispanic.or.Latino..Two.or.More.Races = 'Two or More Races'))
NOFinalData2 <- NOFinalData2 %>% select(FIPS, Race, IncomeBin, Income, IncomePercentile, NewHouseholds, 'Mean Occurence/Year', 'Crime/Capita')
# doing the weighted mean by households
# Sort the dataframe by 'Race' and 'IncomeBin' columns
NOFinalData2 <- NOFinalData2 %>%
  mutate_at(vars(NewHouseholds, `Mean Occurence/Year`, `Crime/Capita`), as.numeric)
NOFinalData2 <- NOFinalData2[complete.cases(NOFinalData2), ]
# Calculate the weighted mean 'CPC' using 'crimes_per_capita' as values and 'num_of_people' as weights
NOFinalData3 <- NOFinalData2 %>%
  group_by(Race, IncomePercentile) %>%
  mutate(CPC = `Crime/Capita`*NewHouseholds)
NOHouseholds <- NOFinalData2 %>%
  group_by(Race, IncomePercentile) %>%
  summarize(TotalHouseholds = sum(NewHouseholds))
NOFinalData3 <- NOFinalData3 %>% 
  group_by(Race, IncomePercentile) %>%
  summarize(CPCxHouseholds = sum(CPC))
NOFinalData3 <- cbind(NOHouseholds, NOFinalData3)
NOFinalData3 <- NOFinalData3 %>% select(Race...1, IncomePercentile...2, TotalHouseholds, CPCxHouseholds)
NOFinalData3 <- rename(NOFinalData3, Race = Race...1, IncomePercentile = IncomePercentile...2)
NOFinalData3$CPC <- NOFinalData3$CPCxHouseholds / NOFinalData3$TotalHouseholds
NOFinalData4 <- NOFinalData3 %>% select(Race,IncomePercentile, CPC)

#combining income bins and transforming to income percentile
NOFinalData5 <- NOFinalData4 %>%
  mutate(IncomePercentile = recode(IncomePercentile, '3.00' = 4.0, '8.15' = 4.0, '12.50' = 14, '17.00' = 14, '21.50' = 23, '25.90' = 23, '30.30' = 32, '34.50' = 32, '38.50' = 41, '44.00' = 41, '52.80' = 59, '64.00' = 59, '74.90' = 79, '82.50' = 79, '88.90' = 93, '96.10' = 93))
NOFinalData5 <- NOFinalData5 %>% 
  group_by(Race, IncomePercentile) %>% 
  summarise(mean_CPC = mean(CPC))
NOFinalData5$mean_CPC_per1000 <- LAFinalData5$mean_CPC*1000
NOFinalData6 <- NOFinalData5[NOFinalData5$Race == "Asian" | NOFinalData5$Race == "Black/African American" | NOFinalData5$Race == "Hispanic/Latino" | NOFinalData5$Race == "White",  ]
#combining certain races
NOFinalData7 <- NOFinalData5 %>%
  mutate(Race = recode(Race, 'American Indian/Alaska Native' = 'Other Race', 'Native Hawaiian/Pacific Islander' = 'Other Race', 'Two or More Races' = 'Other Race'))
NOFinalData7 <- NOFinalData7 %>% 
  group_by(Race, IncomePercentile) %>% 
  summarise(new_CPC = mean(mean_CPC_per1000))
```

```{r figures}
# final graphs, all races, subset, and second subset
NOcrime1 <- ggplot(NOFinalData6, aes(x=IncomePercentile, y=mean_CPC_per1000)) + 
  geom_line(aes(linetype=Race, col=Race), linewidth=.8) + 
  geom_point(aes(col=Race), size=1.5) +
    scale_color_manual(values=c('orange', 'purple3', 'blue4', 'green3')) +
    scale_linetype_manual(values=c("twodash", "solid", "dashed", "dotted")) +
  coord_cartesian(xlim=c(0,100), ylim=c(45, 68)) + 
  labs(title="Income Percentile vs CPC", y="Crimes-Per-1000 Capita", x="Income Percentile") +
  theme(legend.position="bottom", legend.box = "horizontal") +  
  labs(subtitle="Subset of Races") +
  theme(panel.background = element_rect(fill = 'white'),
          panel.grid.major = element_line(colour = "black", size=0.1),
          panel.grid.minor = element_line(colour = "black", 
                                          size=.1),
          panel.border = element_blank(),
          axis.line.x = element_line(colour = "black", 
                                     size=0.1, 
                                     lineend = "butt"),
          axis.line.y = element_line(colour = "black", 
                                     size=.1))
NOcrime2 <- ggplot(NOFinalData5, aes(x=IncomePercentile, y=mean_CPC_per1000)) + 
  geom_line(aes(linetype=Race, col=Race), linewidth=.8) +
  geom_point(aes(col=Race), size=1.5) +
  scale_color_manual(values=c('orange', 'purple3', 'brown', 'blue4', 'pink', 'yellow2', 'grey2', 'green3')) +
  scale_linetype_manual(values=c("twodash", "solid", "dotdash", "dashed", "1F", "12345678", "dashed", "dotted")) +
  coord_cartesian(xlim=c(0,100), ylim=c(43, 70)) + 
  labs(title="Income Percentile vs CPC", y="Crimes-Per-1000 Capita", x="Income Percentile") +
  theme(legend.position="bottom", legend.box = "horizontal") + 
  labs(subtitle="All Races") +
  theme(panel.background = element_rect(fill = 'white'),
          panel.grid.major = element_line(colour = "black", size=0.1),
          panel.grid.minor = element_line(colour = "black", 
                                          size=.1),
          panel.border = element_blank(),
          axis.line.x = element_line(colour = "black", 
                                     size=0.1, 
                                     lineend = "butt"),
          axis.line.y = element_line(colour = "black", 
                                     size=.1))
NOcrime3 <- ggplot(NOFinalData7, aes(x=IncomePercentile, y=new_CPC)) + 
  geom_line(aes(linetype=Race, col=Race), linewidth=.8) +
  geom_point(aes(col=Race), size=1.5) +
    scale_color_manual(values=c('orange', 'purple3', 'red2', 'blue4', 'green3')) +
    scale_linetype_manual(values=c("twodash", "solid", "longdash", "dashed", "dotted")) +
  coord_cartesian(xlim=c(0,100), ylim=c(45,67)) + 
  labs(title="Income Percentile vs CPC", y="Crimes-Per-1000 Capita", x="Income Percentile") +
  theme(legend.position="bottom", legend.box = "horizontal") + labs(subtitle="Second Subset of Races") +
  theme(panel.background = element_rect(fill = 'white'),
          panel.grid.major = element_line(colour = "black", size=0.1),
          panel.grid.minor = element_line(colour = "black", 
                                          size=.1),
          panel.border = element_blank(),
          axis.line.x = element_line(colour = "black", 
                                     size=0.1, 
                                     lineend = "butt"),
          axis.line.y = element_line(colour = "black", 
                                     size=.1))
ggsave("NOgraph_crime_all.pdf", NOcrime2, path = "/Users/alcenchiu/Downloads")
ggsave("NOgraph_crime_subset1.pdf", NOcrime1, path = "/Users/alcenchiu/Downloads")
ggsave("NOgraph_crime_subset2.pdf", NOcrime3, path = "/Users/alcenchiu/Downloads")
```

OLD STUFF
# doing the weighted mean by households
# first sum the total households in each tract by race and income bin
NOFinalData2$Households <- as.numeric(NOFinalData2$Households)
NOsum_of_households <- NOFinalData2 %>%
  group_by(Race, IncomeBin) %>%
  summarize(sum_of_households = sum(Households))
# then multiply the crime-per-capita by number of households for each tract by income bin and race  
NOFinalData2$'Crime/Capita' <- as.numeric(NOFinalData2$'Crime/Capita') #ERROR
NOCPCxHouseholds <- NOFinalData2 %>%
  group_by(Race, IncomeBin) %>%
  mutate(CPCxHouseholds = 'Crime/Capita' * Households) %>%
  summarize(CPCxHouseholds = sum(CPCxHouseholds)) # then sum across each tract
# put these two calculations side by side to do final calculations
NOFinalData3 <- cbind(NOCPCxHouseholds, NOsum_of_households)
NOFinalData3 <- NOFinalData3 %>% select(-one_of('Race...4','Income_Bin...5'))
# divide the previously calculated CPCxHouseholds by household sum to complete weighted mean
FinalData6 <- merge(CPCxHouseholds, sum_of_households, by = c("Race", "Income_Bin")) %>%
  mutate(CPC = CPCxHouseholds / sum_of_households)
# rename income bins to 1-16
# create new column for average income for each bin
FinalData7 <- FinalData6 %>%
  mutate(Income_Bin = recode(Income_Bin, '1' = '5000', '2' = '12500', '3' = '17500', '4' = '22500', '5' = '27500', '6' = '32500', '7' = '37500', '8' = '42500', '9' = '47500', '10' = '55000', '11' = '67500', '12' = '87500', '13' = '112500', '14' = '137500', '15' = '175000', '16' = '240000'))
FinalData7 <- FinalData7 %>% rename_at('Income_Bin', ~'Income')
FinalData7$Income_Bin <- FinalData7$Income
FinalData7 <- FinalData7 %>% relocate('Income_Bin', .after = Race)
FinalData7 <- FinalData7 %>%
  mutate(Income_Bin = recode(Income_Bin, '5000' = '1', '12500' = '2', '17500' = '3', '22500' = '4', '27500' = '5', '32500' = '6', '37500' = '7', '42500' = '8', '47500' = '9', '55000' = '10', '67500' = '11', '87500' = '12', '112500' = '13', '137500' = '14', '175000' = '15', '240000' = '16'))
FinalData7 <- FinalData7 %>% select(-one_of('Income_Percentile'))
# calculate the income percentile of each average income
FinalData7$Income_Percentile <- FinalData7$Income_Bin
FinalData7 <- FinalData7 %>% relocate('Income_Percentile', .after = Income)
FinalData7 <- FinalData7 %>%
  mutate(Income_Percentile = recode(Income_Percentile, '1' = 3.0, '2' = 8.15, '3' = 12.5, '4' = 17.0, '5' = 21.5, '6' = 25.9, '7' = 30.3, '8' = 34.5, '9' = 38.5, '10' = 44.0, '11' = 52.8, '12' = 64.0, '13' = 74.9, '14' = 82.5, '15' = 88.9, '16' = 96.1))
#  create subset of only white, asian, hispanic, and black
FinalData8 <- FinalData7[FinalData7$Race == "Asian" | FinalData7$Race == "Black/African American" | FinalData7$Race == "Hispanic" | FinalData7$Race == "White",  ]